### 2016-09-30 intro-old.tex
intro-old with citations

\section{Introduction}
\paragraph{Basic issues in Naor-Yogev. }
\begin{itemize}
\item The NY paper formalizes and investigates a security notion of limited interest
\item The proposed construction won't scale in common network applications (e.g. large CDN, P2P networks)
\item The main (im)possibility results are of theoretical interest only
\item The basic syntax and operation of their Bloom filter formalization is underdefined.  (This really irritates me.)  It isn’t clear that their Bloom filter formalization actually captures traditional Bloom filters! \tsnote{UPDATE (5/20/16): It is clear, now, that it \emph{does not}.} \tsnote{Also, why isn't the size of the representation somehow a part of the syntax or correctness/soundness conditions?  The fact that the representation is supposed to be small doesn't appear in the syntax anywhere so, syntactically, $B_1(S)=S$ and $B_2(S,x)=1 \Leftrightarrow x \in S$ works just fine, and is trivially secure by their definition! }
\item The ``adversarial-resilient Bloom Filter'' definition does not give the adversary access to the hash functions that created the representation; effectively, they are secret. (No matter if the [NY] syntax does or does not allow them to be encoded in the representation.)  This is odd and does not match reality, e.g. the popular Squid proxy uses plain MD5, splits the output into four chunks, and defines these as four hash functions.  Hardly secret. \tsnote{I did find a setting where Bloom filters use secret keys: privacy-preserving record linkage.  Here one wants to know if two databases contain information about the same person (abstractly, a set of record identifiers); you create a Bloom filter for each record, one for each unique identifier in some cases.  Suggested hash functions are $H_j(x) = g(x) + j\cdot h(x) \bmod m$ for $j=\{0,1,\ldots,k-1\}$, and $g,h$ are (e.g.) HMAC-SHA1 with different keys.  In practice, apparently the~$x$ are bigrams extracted from string identifiers (e.g. ``Thomas''); papers show how to break this ``encrypted'' Bloom filter by recovering a large fraction of names, via (roughly) frequency analysis.}
\item The ``unsteady representation'' does not seem well founded.  Not sure what Bloom filter-like data structures would have randomized querying procedures.  They mention the possibility of differential privacy mechanisms being incorporated into the querying procedure.  But what's the purpose of this, if the security definition gives the adversary the set~$S$?  (What are you keeping private?) 
\end{itemize}

>>>>

%\jnote{Are we being too specific by focusing on hash-based
%set-membership only? It would be nice to give general definitions
%that apply to arbitrary data structures (constructed in arbitrary
%ways) and then only later specialized to hash-based Bloom filters.
%(Put this in an appendix for now, until we see how things play
%out.)}

\section{Introduction}
We revisit the formalization of Bloom filters~\cite{bloom1970space} and closely
related data structures as primitives with explicit security goals.
Recently, Naor and Yogev~\cite{naor2015bloom} (hereafter NY) gave such a
formalization, providing syntax for a generalized abstraction of
Bloom filters, as well as casting the classical Bloom filter
soundness condition as a security experiment admiting adaptive
adversaries.  To briefly summarize, a Bloom filter is a data
structure for compactly representing a set~$\mathcal{S}$ in a way
that supports constant-time responses to set-membership queries. The
representation of~$\mathcal{S}$ is a bit-array~$M$ of length~$m$,
all initially set to~0.  To insert $x \in \mathcal{S}$ into~$M$, one
computes indices $h_1(x),h_2(x),\ldots,h_k(x)$ where each $h_i
\colon \mathcal{U} \to \{0,1,\ldots m-1\}$ maps from a
universe~$\mathcal{U}$ (which contains $\mathcal{S}$) to indices
of~$M$.  The bits at positions $h_1(x),h_2(x),\ldots,h_k(x)$ are set
to 1; if a bit is already 1, due to inserting some previous element
of~$\mathcal{S}$, then it is left alone.  After all elements
of~$\mathcal{S}$ have been inserted, the resulting bit-array~$M$ is
taken as the representation.  To test if $y \in \mathcal{S}$, one
checks if \[(M[h_1(y)]=1 \wedge M[h_2(y)]=1 \wedge \cdots \wedge
M[h_k(y)]=1),\] returning ``yes'' if so, and ``no'' otherwise. Bloom
filters are correct, in the sense that if $y \in \mathcal{S}$, the
set-membership test always returns ``yes''.  The classical soundness
condition asserts that for all $\mathcal{S}$ and any $y
\notin\mathcal{S}$, we have $\Prob{h_1,h_2,\ldots,h_k \getsr
\mathrm{Func}(\mathcal{U},[m])\colon M[h_1(y)]=1 \wedge \cdots
\wedge M[h_k(y)]=1} \leq \epsilon$ where $\epsilon$, the
false-positive error, is a parameter of the Bloom filter.  (The
values of~$\epsilon,m,k$, and $|\mathcal{S}|$ are related in a
well-known way.) NY recast this soundness condition as a game in
which an adversary~$A$ is given~$\mathcal{S}$ and an oracle for
set-membership queries, and it attempts to find one or more false
positives. The fact that~$A$ can \emph{adapt} its queries and its
output based on what it learns from the set-membership oracle (but,
as we will see, not upon the hash functions) is the key definitional
contribution of~NY.

Bloom filters have a broad range of practical applications, for example, in content-distribution networks, large database query processing, routing algorithms for peer-to-peer networks, protocols for establishing linkages between medical-record databases, fair routing of TCP packets, Bitcoin wallet synchonization. \tsnote{need citations} Given that NY is addressing such a useful real-world object, we find their formalism, both the syntax and security notions, to be less precise and useful than one would want.  Let us explain.

Syntactically, NY says a Bloom filter (with a steady representation) is a pair of algorithms $\mathbf{B}=(\mathbf{B}_1, \mathbf{B}_2)$. The setup algorithm~$\mathbf{B}_1$ is randomized, and on input a set~$\mathcal{S}$ it returns a representation~$M$ (from some undefined, implicit set of representations).  The query algorithm~$\mathcal{B}_2$ is deterministic, and on input a representation~$M$ and an element~$x \in \mathcal{U}$, it returns a bit.  For correctness they make the classical demand, that for all $x \in \mathcal{S}$ we have $\Prob{\mathbf{B}_2(\mathbf{B}_1(\mathcal{S}),x)=1}=1$.  For soundness, adversary~$A$ plays the following game, ``Adversarial-resilient Bloom Filter with a steady representation''. First, $M \getsr \mathbf{B}_1(\mathcal{S})$ for some set $\mathcal{S}$ that can be adversarially chosen. Then the adversary may make queries $x_1,x_2,\ldots,x_q$ to an oracle for $\mathbf{B}_2(M,\cdot)$.  At the end of its execution, the adversary outputs~$x^*$ and wins the game if (1) $x^* \not\in \mathcal{S} \cup \{x_1,x_2,\ldots,x_q\}$, and (2) $\mathbf{B}_2(M,x^*)=1$.

First, we note that the security notion forbids~$A$ to win if it outputs $x^* \in \{x_1,x_2,\ldots,x_q\}$, even if one of these was a false positive.  On one hand, this notion is unsatisfying because it would not say that an attacker wins by creating (say) a bogus email address, and then observing that it passes a spam filter that is based on a Bloom filter represention of a whitelist.\footnote{This is one of the motivating examples from NY.}  The attacker is only allowed to win if it finds a false-positive that it has not verified.  On the other hand, the NY notion does seem to capture the intuition that finding additional false positives does not become easier as more are learned.  Our notions will address both sides of this discussion.
%
%\jnote{We discussed this on the phone, but let me put it in writing here. I think this is actually a reasonable choice because it captures the notion that ``even after finding some false positives, it remains hard to find additional false positives.'' Note that in practice finding false positives is ``easy'' since $\epsilon$ might be $1/1000$ rather than negligible.}
%
%\tsnote{For me the question is: is security violated once the first FP is found, or the second? My answer, which is in line with the traditional soundness notion, is that the first FP is a security violation even if finding it isn't ``hard'' by cryptographic standards. But I do appreciate your point.  A natural goal is to say that, in some sense, \emph{adaptivity doesn't make it any easier} to find a FP.  Adapting to what, though? In the traditional notion, $x$~is picked before the coins of~$\mathbf{B}_1$ are flipped, i.e., before the hash functions are sampled.  The direct non-adaptive generalization is to say that $x_1,x_2,\ldots,x_q$ are all picked up front.  The direct \emph{adaptive} generalization would allow $x_1,x_2,\ldots,x_q$ to depend in the coins of~$\mathbf{B}_1$, i.e., the hash functions.  The NY definition captures only indirect dependence: adversaries that can adapt to set-membership queries, but \emph{not} (directly) to the input-output behaviors of the hash functions.  The three notions I've proposed in Figure 1 cover a spectrum of adaptivity: the first is adapting to set-membership queries only, the second to those and hash input-output behavior, the third to set-membership queries and full knowledge of the hash functions.  Each has it's own associated (informal) security interpretation.}
%\tsnote{Perhaps a more obvious way to capture the idea that ``finding some FPs doesn't help find additional ones'' is to parameterize my notion(s) with a number~$f$, and say that that the adversary wins iff it outputs~$f$ FPs (these may have been previously queried to the set-membership oracle). Note that in the ROM (and probably in practice) finding~$f>1$ FPs will require~$f$ times the work.  Right?}
%
%\tsnote{FYI: this is how MAC security against multiple forgeries is defined.  See \texttt{https://eprint.iacr.org/2006/095.pdf} for details.}

Second, we note that the NY syntax does not capture the size of~$M$
as a parameter; \jnote{I think this is also reasonable; typically
security is defined without regard for efficiency} \tsnote{My
complaint isn't about efficiency. It's about the fact that, by not
including $|M|$ in the definition, the trivial scheme I give (just
below) is allowed, and is secure.  Anyway, as I say at the end of
this paragraph, this is a small(er) complaint than what follows}.
\jnote{I would say that the trivial scheme \emph{is} secure!}
\tsnote{Okay, well then we need some way to ``rule out'' the trivial
solution. Perhaps just in the text -- yes, the trivial scheme works,
but it isn't interesting in practice. Also, in the concrete security
bounds that we will prove, the size of the representation is going
to come up, e.g.\ the number of bits in the BF array directly affect
the FP rate. Hence it makes sense to say things like ``an
$(n,k,m)$-filter\ldots'' where $m$ is the size of the
representation.} \jnote{I still disagree: efficiency is orthogonal
to functionality and security.} \fixme{
Let's discuss this verbally, because I feel like we are talking past each other.}The surrounding text does say that
$\mathbf{B}_1$ ``outputs a compressed representation [of
$\mathcal{S}$] $\mathbf{B}_1(\mathcal{S})=M$'' but what exactly this
means is never addressed. The formal syntax admits
$\mathbf{B}_1(\mathcal{S})=\mathcal{S}$ and
$\mathbf{B}_2(\mathcal{S},x)=1 \Leftrightarrow x \in \mathcal{S}$,
which is also trivially secure by their definition.  These are both
small, but important complaints. But a larger complaint, and one
that is much harder to see, is that that it is not clear that the NY
formalism actually captures real world Bloom filters.

In particular, say we implement a classic Bloom filter.  Then the hash functions $h_1, h_2, \ldots, h_k$ are either sampled from some family~$\mathcal{H}$ by~$\mathbf{B}_1$ (recall that this algorithm is randomized), or they are hard-coded into the description of~$\mathbf{B}_1$.  Let's assume the former for the moment.  In order for~$\mathbf{B}_2$ to be able to respond to set-membership queries, it must have $h_1,h_2,\ldots,h_k$ as well. Since~$\mathbf{B}_2$ receives only the representation~$M$ as input, it must be the case that $h_1,h_2,\ldots,h_k$ are encoded into~$M$ somehow.  But the text strongly suggests, in several places, that~$M$ does \emph{not} include these.  Both NY and classical analysis of Bloom filters speak of the number of bits used to represent the set~$\mathcal{S}$: the classical analysis means only the number of bits in the actual array, and NY make comparisons throughout between the number of bits~$m$ used by their instantiations and the classical bounds. Moreover, the Bloom filter they construct in one of their main positive results clearly \emph{does not} count as part of the representation size the hash functions used to indicate array locations.
%Thus, if we assume that
%$\mathbf{B}_1$ is sampling $h_1,h_2,\ldots,h_k$, it seems that their
%formalization fails to capture the basic Bloom filter construction;
%at best, it is hard to see clearly that it does.

%\jnote{FWIW, I think the classical description of Bloom filters has the same problem. I.e., if the hash functions are not fixed, then their description should be counted as part of the length of the data structure. On the other hand, if they are fixed, then the false-positive rate is not well-defined (since there is no probability space to speak of). So in that sense, NY just carried over the problem from the classical literature.}
%
%\tsnote{One can suggest that it \emph{should} be counted in the classical description, but the fact is that it isn't :) And in the 30+ years since the original paper, no one saw fit to correct this? From an algorithmic perspective, I think the classical approach makes sense.  The questions being answered are: how many bits do I need to store a representation of the set for a given FP rate, and how does this compare to the combinatorially computed lower-bound? The description length of the hash functions may be bigger or smaller, but the number of bits you need to hold the set representation is independent of that.  (Imagine that you have long random bitstrings in the set~$\mathcal{S}$.  Then whether your hash functions simply truncate, or they are random oracles, the size of the representation as a function of the target FP rate doesn't change.  Yet the description lengths of the hash functions are drastically different.)}

On the other hand, assume the hash functions are implicitly hard-coded into~$\mathbf{B}_1$ (and $\mathbf{B}_2$). Then we can treat~$\mathbf{B}_1$ as deterministic, since it will simply carry out the steps required to populate an array using these hash functions, and output the array~$M$ as the representation.  If the descriptions of~$\mathbf{B}_1,\mathbf{B}_2$ are known to the adversary, who is also provided with~$\mathcal{S}$, then the adversary can compute~$M$ itself, as well as test for false positives itself. So it isn't clear how the security notion helps to reason about difficulty of finding a false-positive. Moreover, NY stresses (at least once) that the representation is \emph{not} given to the adversary in their notions.  So it seems unlikely that they intended for $h_1,h_2,\ldots,h_k$ to be hard-coded into the algorithms.
\jnote{Perhaps it is reasonable to consider a definition in which the set is not given to the adversary?}
\tsnote{A FP security notion? Yes, perhaps so.  It's probably a more realistic notion anyway -- is a spammer really going to know my whitelist a priori? (If he does, I probably have bigger problems in my system than receiving new spam email.) Or set of URLs cached by a CDN server?}

Continuing on this point, it seems that the coins of~$\mathbf{B}_1$ (whatever their use) are intended to be kept secret from the adversary.  Thus, to the extent that it addresses real Bloom filters at all, the NY security notion only addresses applications in which the representation is created using secret coins.  But many real-world applications of Bloom filters have no secrets.  NY point to web proxies, which use Bloom filters to compactly represent the objects they store locally, as motivation for their work.  But real web proxies like Squid~\cite{xxx} do \emph{not} use secrets in their Bloom filters.  Squid, in particular, uses the basic Bloom filter with four hash functions, defined as follows: $h_1(x) = \mathrm{MD5}(x)[0,\ldots,31]$, $h_2(x)=\mathrm{MD5}(x)[32,\ldots,63]$, $h_3(x)=\mathrm{MD5}(x)[64,\ldots,95]$, and $h_4(x)=\mathrm{MD5}(x)[96,\ldots,127]$.  Likewise, there are no secrets in the Bloom filters used by Google's BigTable~\cite{xxx}, HBase~\cite{xxx}, \tsnote{make an impressive list.}

There are applications in which the proposed Bloom filter instantiations do use secretly keyed hash functions, e.g. $h_j(x) = (f(K_0,x) + j\cdot g(K_1,x))\bmod m$, where $j\in[1,k]$, $m$ is the number of bits in the array, and where $f,g$ are PRFs keyed by secrets $K_0,K_1$. This particular ``encrypted Bloom filter'' instantiation was suggested for use in efficient linking of records across separate medical record databases~\cite{schnell2011novel}.  (It was subsequently shown not to be secure by Niedermeier et al.~\cite{niedermeyer2014cryptanalysis}, where a clever use of frequency analysis recovered the last names of patients given access only to the Bloom filter array.)
In any case, it is clear that the NY definition does not capture the most widely used applications of Bloom filters, e.g. CDN summary caches, P2P network routing algorithms, etc.
%\tsnote{Could also point out that their positive results use constructions that have secret keys, and these are unlikely to be of any use in major applications like CDNs or P2P networks.  But maybe the horse is sufficiently beaten by now...}

%\tsnote{What about content-based routing, or whatever that field is calling itself now?  A Bloom filter seems likely to be used there, and you'd want privacy for at least the content-seeker.}

\heading{Our contributions. }
Given these shortcomings and the prevalent use of Bloom filters in practice, we revisit the matter of formalizing them as primitives with explicit security goals, these goals being abstracted from the attack surface they expose in practice.   We begin by giving a new syntax for hash-based filters, which more clearly captures Bloom filters...

We generalize this syntax to hash-based filters that are mutable,
%\jnote{I find ``mutable'' a slightly awkward term, maybe because it makes me think of mutability in the context of programming languages. In much data structures literature, this is called the ``dynamic'' case, in contrast to the ``static'' case.}
%
%\tsnote{I adopted this term after reading it in some bloom filter paper(s). Ironically, I liked it for the same reason you think it is awkward :) My PL association to the term is that an immutable object is one whose state cannot be modified after it is created, and a mutable object is the opposite.  But I don't really care too much.}
in the sense
that they allow for updating of the representation. This allows us
to capture counting Bloom filters, spectral Bloom filters, stable
Bloom filters, count-min sketches, and other compact set
representation data structures...

We provide various security notions for these primitives... FP with private, public representation coins; set privacy with private, public representation coins; FP/set privacy in the multi-representation setting (outsider attack, think CDNs); FP/set privacy in the multi-representation setting with corruptions (insider attack, think P2P networks) \tsnote{Those are just the ones that come to mind now.  Could also consider authenicity of representations, think CDN or P2P settings.}

We show that...

\heading{Related work: attacks}
\begin{itemize}
\item Niedermayer et al., ``Cryptanalysis of Basic Bloom Filters Used for Privacy-Preserving Record Linkage'', breaking privacy of secret-hash-function Bloom filters. \tsnote{Journal of Privacy and Confidentiality, 2014}
\item Gerbet, Kumar and Lauradoux, ``The power of evil choices in bloom filters''.  \tsnote{DSN'15: Looks like a real goldmine of related work!}
\item Crosby and Wallach, ``Denial of Service via Algorithmic Complexity Attacks'' \tsnote{Gives attacks on Squid}
\item Gao et al., ``Internet Cache Pollution Attacks and Countermeasures''
\end{itemize}

\heading{Related work: definitions(?)}
\begin{itemize}
\item Nojima and Kadobayashi, ``Cryptographically Secure Bloom Filters''. \tsnote{Gives some security definitions for privacy. Quick scan, not super clear what they achieve. The definition of client-privacy (Definition 1) for example, makes no sense to me.  Actually, likewise for server-privacy (Definition 2).  Both seem vague and thoroughly underspecified.}
\item Naor and Yogev
\item Eujin Goh, ``Secure Indexes'' \tsnote{A secure index can
    be used for set membership.  Builds a secret-key data
    structure (an Index) that allows searching for keyword~$w$
    if one holds the trapdoor $T_w$ for~$w$, where the trapdoor
    depends on the secret key.  Main construction uses
    traditional Bloom filters and a PRF.  Construction appears
    quite inefficient, needing a very long secret key, turning a
    keyword~$w$ into a bunch of PRF outputs, and then storing
    each of these PRF outputs in the BF.  Havent read the full
    analysis; don't know if this was ever published. }
    \jnote{Never published. I think this work uses Bloom filters
    for encrypted search; I don't remember the paper having much
    to say about Bloom filters themselves.}
\end{itemize}

\heading{Related work: constructions}
\begin{itemize}
\item Bellovin and Cheswick, ``Privacy-Enhanced Searches Using
    Encrypted Bloom Filters''.
\item Kerschbaum , ``Public-Key Encrypted Bloom Filters with Applications to Supply Chain Integrity''.
\item S\"{a}rell\"{a} et al., ``BloomCasting: Security in Bloom Filter Based Multicast''.
\item Dong, Chen, Wen, ``When Private Set Intersection Meets Big Data: An Efficient and Scaleable Protocol'' \tsnote{``garbled bloom filters'', which actually store the set element by storing~$k$ xor-shares, one at each of the~$k$ hash indices (with care for reusing shares if hash collisions occur); also and``oblivious bloom intersection''}\tsnote{If the filter and the hash functions are public, there is a naive attack that works for some interesting parameters.  Pick~$k$ positions $i_1,i_2,\ldots,i_k$, xor strings at these positions to get a candidate~$x$.  If $h_{1}(x)=i_1 \wedge h_2(x)=i_2 \wedge \cdots \wedge h_k(x) = i_k$ then either $x \in S$ or~$x$ is a false-positive. (You don't have to do all~$k$ hashes, you can stop as soon as one fails to match the index.) Say you have a 1000-position filter ($m=1000$) and a 100-element set ($n=100$), and you are willing to tolerate a 1\% FP rate.  Then you'd set $k=4$ (a la Squid).  There are roughly $2^{35}$ subsets of 4 indices to consider, which is reasonable on a laptop these days.  (Also, since $n=100$ the expected number of trials is roughly $2^{28}$.) With the FP rate of 1\%, if you find a winner then almost certainly it is in the set.  Granted, this attack is naive, but notice that you \emph{cannot} mount it against a standard Bloom filter. Also notice that this attack might be significantly more efficient than brute force guessing over the universe of inputs (imagine that $U=\bits^{64}$), even if you know that the distribution deviates significantly from uniform. }
\item Tarkoma, Rothenberg, Lagerspetz ``Theory and Practice of Bloom Filters in Distributed Systems'' \tsnote{Great high-level coverage.  Only found preprint version though.}
\item Durham, Kantarcioglu, Xue, Kuzu, Malin ``Composite Bloom Filters for Secure Record Linkage'' \tsnote{Per-field BFs, sampled and composed into single BF that is then permuted by a secret random permtation.  No clear statement of the problem that is being solved.  Should pull full version and get details.}
\end{itemize}

\heading{Related work: tangential}
\begin{itemize}
\item Chang and Mitzenmacher ``Privacy Preserving Keyword Searches on Remote Encrypted Data''.
\item Mitzenmacher and Vadhan. ``Why Simple Hash Functions Work: Exploiting the Entropy in a Data Stream''.
\item Dodis et al. ``Fuzzy Extractors: How to Generate Strong Keys from Biometrics and Other Noisy Data'' \tsnote{Introduces ``secure sketches'', which is a representation of a single-element set that is information theoretically private (up to some function of the min-entropy of the element); only tangentially related to ``sketches'' as defined in the Bloom filter literature.}
\end{itemize}

\if{0}
\paragraph{Basic issues in Naor-Yogev. }
\begin{itemize}
\item The NY paper formalizes and investigates a security notion of limited interest
\item The proposed construction won't scale in common network applications (e.g. large CDN, P2P networks)
\item The main (im)possibility results are of theoretical interest only
\item The basic syntax and operation of their Bloom filter formalization is underdefined.  (This really irritates me.)  It isn’t clear that their Bloom filter formalization actually captures traditional Bloom filters! \tsnote{UPDATE (5/20/16): It is clear, now, that it \emph{does not}.} \tsnote{Also, why isn't the size of the representation somehow a part of the syntax or correctness/soundness conditions?  The fact that the representation is supposed to be small doesn't appear in the syntax anywhere so, syntactically, $B_1(S)=S$ and $B_2(S,x)=1 \Leftrightarrow x \in S$ works just fine, and is trivially secure by their definition! }
\item The ``adversarial-resilient Bloom Filter'' definition does not give the adversary access to the hash functions that created the representation; effectively, they are secret. (No matter if the [NY] syntax does or does not allow them to be encoded in the representation.)  This is odd and does not match reality, e.g. the popular Squid proxy uses plain MD5, splits the output into four chunks, and defines these as four hash functions.  Hardly secret. \tsnote{I did find a setting where Bloom filters use secret keys: privacy-preserving record linkage.  Here one wants to know if two databases contain information about the same person (abstractly, a set of record identifiers); you create a Bloom filter for each record, one for each unique identifier in some cases.  Suggested hash functions are $H_j(x) = g(x) + j\cdot h(x) \bmod m$ for $j=\{0,1,\ldots,k-1\}$, and $g,h$ are (e.g.) HMAC-SHA1 with different keys.  In practice, apparently the~$x$ are bigrams extracted from string identifiers (e.g. ``Thomas''); papers show how to break this ``encrypted'' Bloom filter by recovering a large fraction of names, via (roughly) frequency analysis.}
\item The ``unsteady representation'' does not seem well founded.  Not sure what Bloom filter-like data structures would have randomized querying procedures.  They mention the possibility of differential privacy mechanisms being incorporated into the querying procedure.  But what's the purpose of this, if the security definition gives the adversary the set~$S$?  (What are you keeping private?)
\end{itemize}
